Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-07 paper-kelompok/main.tex
Add UI image captions

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.27]{system-dfd.png}}
    \caption{Level-1 Data Flow Diagram (DFD) of the system.}
    \label{system-dfd}
    \end{figure}

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.27]{dmf-hardware-scheme.png}}
    \caption{The main components of the proposed device.}
    \label{dmf-hardware-scheme}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{light-source-dfd.png}}
    \caption{DFD of the light source subsystem.}
    \label{light-source-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.33]{light-sensor-dfd.png}}
    \caption{DFD of the light sensor subsystem.}
    \label{light-sensor-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.35]{fsm.png}}
    \caption{FSM diagram of the portable visible spectrophotometer.}
    \label{fsm}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.43]{ui-dfd.png}}
    \caption{DFD of the user interface subsystem.}
    \label{ui-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{power-dfd.png}}
    \caption{DFD of the power subsystem.}
    \label{power-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{hardware-2.jpg}}
    \caption{Overview of the device's internal components.}
    \label{hardware}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{lcd-spectrum.png}}
    \label{lcd-spectrum}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{lcd-table.png}}
    \label{lcd-table}
    \end{figure}

>>>>

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.27]{system-dfd.png}}
    \caption{Level-1 Data Flow Diagram (DFD) of the system}
    \label{system-dfd}
    \end{figure}

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.27]{dmf-hardware-scheme.png}}
    \caption{The main components of the proposed device}
    \label{dmf-hardware-scheme}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{light-source-dfd.png}}
    \caption{DFD of the light source subsystem}
    \label{light-source-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.33]{light-sensor-dfd.png}}
    \caption{DFD of the light sensor subsystem}
    \label{light-sensor-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.35]{fsm.png}}
    \caption{FSM diagram of the portable visible spectrophotometer}
    \label{fsm}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.43]{ui-dfd.png}}
    \caption{DFD of the user interface subsystem}
    \label{ui-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{power-dfd.png}}
    \caption{DFD of the power subsystem}
    \label{power-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{hardware-2.jpg}}
    \caption{Overview of the device's internal components}
    \label{hardware}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{lcd-spectrum.png}}
    \caption{The display of the spectrum page of a spectrum-mode measurement}
    \label{lcd-spectrum}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{lcd-table.png}}
    \caption{The display of the table page of a quantization-mode curve}
    \label{lcd-table}
    \end{figure}
